\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Bernard Swanepoel} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+27(083) 576-6275 \\ South Africa, North West, Stilfontein} 
\address{\href{mailto:BernardSwanepoel1510@gmail.com}{Email} \\ \href{https://www.linkedin.com/in/bernard-swanepoel-a2777322b/}{LinkedIn} \\ \href{https://xoxothefrozenfox.github.io/BernardSwanepoelCV/}{CV} \\ \href{https://xoxothefrozenfox.github.io/react-personal-portfolio/}{Portfolio}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software Engineer with development experience, seeking full-time Full-stack developer roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf MSc Computer Science}, North-West University \hfill {2025-2027}

{\bf BSc Hons Computer Science and Information technology}, North-West University \hfill {2024}\\
Relevant Coursework: Decision support systems, Databases,  Computer security, and Artificial intelligence.

{\bf BSc Information Technology}, North-West University \hfill {2020 - 2023}\\
Relevant Coursework: Data structures and algorithms, IT Developments, Computer networks, Operating Systems, Systems Analysis and Design, Object Oriented Programming, Information Security, and Structured Programming.
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Python, Java, C\texttt{\#}, Bash, HTML, CSS, JavaScript, \LaTeX, AWS, Kotlin, GitHub, Linux
\\
Frameworks & Node.js, React, Flask, TensorFlow, PyTorch, FastAPI, Ionic, Angular, Spring Boot, .NET\\
Soft Skills & Creative, Teamwork, Adaptability, Problem-solving\\
Other skills & Marketing, Business, Management, Tutoring\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Marketing Staff} \hfill Sep 2023 - Present\\
Nuwelco \hfill \textit{South Africa, North West, Stilfontein}
\begin{itemize}
    \itemsep -3pt {} 
    \item Assisting Nuwelco in marketing their manufacturing products.
    \item Brought Nuwelco to the attention of a much larger audience via LinkedIn marketing \href{https://www.linkedin.com/company/98936614/admin/feed/posts/}{(Check page)}.
\end{itemize}

\textbf{CMPG 212 Tutor} \hfill Feb 2023 - Jun 2023\\
North-West University \hfill \textit{South Africa, North West, Stilfontein}
\begin{itemize}
    \itemsep -3pt {} 
    \item Conducted tutoring sessions to support individuals facing challenges with the given programming practicals.
    \item I created videos to assist students who were too shy to ask questions and made myself available on WhatsApp to answer any queries as needed.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Angular Ionic Weather Web App:} {Created a responsive weather web app with Angular and Ionic, leveraging weatherAPI for real-time, location-based data. Styled with SCSS, integrated GPS, and hosted on Netlify with GitHub for version control. \href{https://extraordinary-eclair-8e48b9.netlify.app/}{(Netlify link)}}.
\item \textbf{Dog breed classification:} {Used TensorFlow, Jupyter Notebooks, and Python to create a deep learning model that can classify dog breeds \href{https://github.com/XoXoTheFrozenFox/Dog_Breed_Classfication}{(Check GItHub page)}}.
\item \textbf{Spring Boot Micro Service:} {Developed a Spring Boot microservice with Neo4j Aura, using Java, Maven, GitHub Actions, AWS CDK with JavaScript/NPM for IaC, and tested with Postman. Executed Cypher queries and managed code in GitHub with IntelliJ and VSCode.
}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Other Activities} 
\begin{itemize}
    \item Music: I play the violin and piano and have a passion for singing opera.
    \item Technology: I enjoy building computers and experimenting with 3D printing.
    \item Games: In my free time, I like to play video games.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\end{document}
